Tom Stafford

### 2024-02-05 index.qmd
wip

![](tom_2020.jpg){width="20%"}

@@

At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research. As Research Practice Lead, I represent the University of Sheffield as Institutional Lead for the UK Reproducibility Network, and chair of the national UKRN Institutional Leads group.

As Senior Fellow at the [Research on Research Institute](https://researchonresearch.org/), I lead the programme [AFIRE: Accelerator For Innovation &amp; Research Funding Experimentation](https://researchonresearch.org/project/a-f-i-r-e/).

@@

This page is a test. Most current material is at [tomstafford.sites.sheffield.ac.uk](https://tomstafford.sites.sheffield.ac.uk/)

>>>>

![](tom_2020.jpg){width="25%"}

@@

At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research. As Research Practice Lead, I represent the University of Sheffield on the UK Reproducibility Network, and chair the national UKRN Institutional Leads group.

As Senior Fellow at the [Research on Research Institute](https://researchonresearch.org/), I lead the programme [AFIRE: Accelerator For Innovation &amp; Research Funding Experimentation](https://researchonresearch.org/project/a-f-i-r-e/). We seek to catalyse the generation and use of high quality evidence on research processes ("Metaresearch").

@@

These pages are intended to replace [tomstafford.sites.sheffield.ac.uk](https://tomstafford.sites.sheffield.ac.uk/), and will reflect my professional activities.

My non-professional activities are recorded on my personal blog at <https://idiolect.org.uk/notes/>
